Contention Management for 5G

### 2017-04-12 article/article.tex
toujours buggé
res without wt

   \subsection{Problems}

@@

	\subsubsection{Exhaustive generation}
% 	\begin{algorithm}[H]
% 	\caption{Exhaustive Generation}  
% 	\begin{algorithmic}
% 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
% 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
% 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
% 	\FORALL{source $s_i$ in S}
% 	\FORALL{j in Free-Intervals }
% 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
% 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
% 	\STATE Split the Free-Intervals considering the new packet
% 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
% 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
% 	\STATE call Exhaustive Generation on remaining routes
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% 
% 
%       \end{algorithmic}
%       \end{algorithm}

@@

    \subsubsection{Results}
      The following performance evaluation results compares the previous algorithms. Since we try to find a linear time algorithm for the problem PALL, Exhaustive Generation is not a good solution. However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a linear complexity. We tried to determine which algorithm gives a solution with the minimal period.
      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context.
      \paragraph{Short routes}
      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(r_{s_i}) < 2100$ slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.

      For each algorithm, we made a linear research of the minimal period for which, there is a solution on the given instance. The following figure shows us the average periods on 1000 graphs, for a growing number of routes.
      The results of the Exhaustive generation can be considered as a lower bound, indeed, for a given period, this algorithm finds the solution, if it exists.
      As an information, we drew the $\tau.n$ (i.e. the size taken by the messages in the period) and the $2.(\tau.n) $ lines.

@@

      Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route. The following figure shows us the success rate of the algorithms, for 8 routes of size between 0 and 60000 slots, according to the period.

       \begin{center}
      \includegraphics[scale=0.4]{echec_longues.pdf}
      \end{center}

      As we can see, the Shortest longest has a very low success rate, because of the distribution of the size of the routes is now broader, so is the required period.
      Whereas, the Geedy 3NT gives us solutions with much lower period than Shortest Longest.
      Because of it's polynomial complexity, the Exhaustive generation can freeze the simulation when the solution is not easy to find. Thus, we let it stop after a defined number of calculation. 
      The Exhaustive Generation curve gives us the solution when the algorithm has found a solution, and the Upper bound gives us the number of found solutions plus the number of time the algorithm stopped. The real Upper bound is probably between those two curves.

>>>>

   \subsection{Problems}\label{nonmonotone}

@@

	\subsubsection{Exhaustive search}
% 	\begin{algorithm}[H]
% 	\caption{Exhaustive Generation}  
% 	\begin{algorithmic}
% 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
% 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
% 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
% 	\FORALL{source $s_i$ in S}
% 	\FORALL{j in Free-Intervals }
% 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
% 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
% 	\STATE Split the Free-Intervals considering the new packet
% 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
% 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
% 	\STATE call Exhaustive Generation on remaining routes
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% 
% 
%       \end{algorithmic}
%       \end{algorithm}

@@

    \subsubsection{Results}
      The following performance evaluation results compares the previous algorithms. Since we try to find a polynomial time algorithm for the problem PALL, Exhaustive Generation is not a good solution. However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity. We tried to determine which algorithm gives a solution with the minimal period.
      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context.
      \paragraph{Short routes}
      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU. The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route. The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.

      To find the minimal period on a given instance with an algorithm, it is necessary to run the algorithm with some different periods and take the shortest one that does not fail. Since the existence of a $(P-\tau)-periodic affectation)$ is not monotone with regard to P (see section \ref{nonmonotone}), a dichotomous search is not appropriate. Thus, for each algorithm, we made a linear search of the minimal period for which, there is a solution on the given instance. The following figure shows us the average periods on 1000 graphs, for a growing number of routes.
      The results of the Exhaustive generation can be considered as a lower bound, indeed, for a given period, this algorithm finds the solution, if it exists.
      As an information, we drew the $\tau.n$ (i.e. the size taken by the messages in the period) and the $3.(\tau.n) $ lines.

@@

      Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route. The following figure shows us the success rate of the algorithms, according to the period, for 8 routes in which  $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 30000 slots, that correspond to have the size of the route and the period approximately in the same order of magnitude.

      By increasing the size of the routes, the cuts of the exhaustive search, are less efficient. Thus, we defined a counter that allow the search to end if no solution are found. On the following figure, the upper bound represents the cases in which the exhaustive search found a solution plus the number of {\em early} halts of the search. The real upper bound is probably between those two curves.

      The reason why the shortest longest were optimal in the previous experiences (i.e. having routes shorter than message size) is no longer reviewed. We can also imagine that sending the shortest route first on long routes significantly increases the period, because there will be a lot of lost size in the backward and forward periods.

      One the other hand, one can imagine that the greedy $3n\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
       \begin{center}
      \includegraphics[scale=0.4]{echec_longues.pdf}
      \end{center}

      As we can see, the Shortest longest has a very low success rate, because of the distribution of the size of the routes is now broader, so is the required period.
      Whereas, the Geedy 3NT gives us solutions with much lower period than Shortest Longest. The exhaustive search keeps finding good solutions in short periods but it fails a lot for periods until $2.n.\tau$.
